Linear stability of magnetized massive protoplanetary disks

### 2014-04-03 paper/results_azi.tex
first rough draft done

Introducing $B_y = B_z$ leads to an exchange in the mode
characters. For $k_xH\lesssim 0.9$ the modes on the two MRI branches
are similar to the vertical field case. However, for $k_xH\gtrsim0.9$ 
the upper MRI mode transitions to GI, for which $E_m(0)$ is a
minimum; and the lower MRI mode has $E_m(0)$ being a maximum. 
%interchange possible because of GI branch

@@

Notice in Fig. \ref{compare_growth3_tilted_resis} the disappearence of
magnetic modes as $B_y$ is increased. For $B_y=2B_z$, MRI and GI
operate at distinct scales. This implies that regions unstable to GI
cannot develop MRI.

@@

\begin{figure}
  \includegraphics[width=\linewidth,clip=true,trim=0cm 0cm 0cm
    0cm]{figures/result_tilted_resis.ps}
  \caption{Overstable MRI mode in an isothermal resistive disk with
    $Q=0.18 (Q_\mathrm{2D} = 0.67)$, $\Lambda_0=0.1$ and $\beta=100$. 
    The mode has a real frequency $\omega = 0.059\Omega$, or
    $\omega/\gamma \simeq 0.2 $.   
    \label{result_tilted_overstable}}
\end{figure}

>>>>

Introducing $B_y = B_z$ leads to an exchange in the mode
characters. For $k_xH\lesssim 0.9$ the modes on the two MRI branches
are similar to the vertical field case. However, for $k_xH\gtrsim0.9$ 
the upper MRI mode transitions to GI, for which $E_m(0)$ is a
minimum; and the lower MRI mode has $E_m(0)$ being a maximum. 
%We
%believe this interchange is enabled by the presence of GI. 
%interchange possible because of GI branch

@@

Notice in Fig. \ref{compare_growth3_tilted_resis} the disappearence of
magnetic modes between $0.8\lesssim k_xH\lesssim 1.5$ as $B_y$ is
increased. For $B_y=2B_z$, MRI and GI operate at distinct radial
scales. This implies that perturbations unstable to GI cannot develop
MRI.

@@

\begin{figure}
  \includegraphics[width=\linewidth,clip=true,trim=0cm 0cm 0cm
    0cm]{figures/result_tilted_resis.ps}
  \caption{Overstable MRI mode in an isothermal resistive disk with
    $Q=0.18$ ($Q_\mathrm{2D} = 0.67$), $\Lambda_0=0.1$ and $\beta=100$. 
    The mode has a real frequency $\omega = 0.059\Omega$, or
    $\omega/\gamma \simeq 0.2 $.   
    \label{result_tilted_overstable}}
\end{figure}

### 2014-04-03 paper/summary.tex
first rough draft done

Physically, we expect MRI to only interact with self-gravity when
their spatial scales are similar. Because self-gravity acts globally in the
vertical direction, for it to affect the MRI, future non-linear
simluations should consider parameter regimes in which the MRI is
vertically global. Indeed, in the setup of \cite{kim03}, the disk
scale height exceeds the MRI vertical wavelength and self-gravity has
little effect.

@@

%spiral arms, GI angular mometum distribution 
\emph{Beyond axisymmetry.} It is well known that self-gravitating
disks can be unstable to non-axisymmetric perturbations but stable
against axisymmetric perturbations \citep{papaloizou89,papaloizou91}.

>>>>

Physically, we expect MRI to interact with self-gravity when
their spatial scales are similar. Because self-gravity acts globally in the
vertical direction, for it to affect the MRI, future non-linear
simluations should consider parameter regimes in which the MRI is
vertically global. Indeed, in the setup of \cite{kim03}, the disk
scale height exceeds the MRI vertical wavelength and self-gravity has
little impact.

@@

%not looked at how MRI affects GI -> it doesn't because GI isn't
%concerned with shear. only magnetic pressure. maybe a plot of GI with
%magnetic perturbations?

%spiral arms, GI angular mometum distribution 
%global modes 
%compressible term in y-induction equation 
\emph{Beyond axisymmetry.} Axisymmetric perturbations, as we have
assumed, preclude gravitational torques \citep{lynden-bell72}. 
%In 
%order to investigate how angular momentum transport 
The local non-axisymmetric stability of magnetized self-gravitating
thin disks has been considered by several authors
\citep{elmegreen87,gammie96,fan97,kim01}. However, two-dimensional models
exclude the MRI. It will be neccessary to generalize these studies to
3D in order to investigate the impact of the MRI on angular momentum
transport by gravitational instability. Furthermore, self-gravitating
disks can develop global spiral instabilities while stable against local 
axisymmetric perturbations \citep{papaloizou89,papaloizou91}. Global
non-axisymmetric linear models will be desirable to support non-linar
simulations of this kind \citep{fromang04c,fromang05}.

%Our linear problem assumes a non-zero
%vertical field is always present. It is of interest to 
%consider the opposite limit of purely toroidal fields. Of course, one
%must consider the non-axisymmetric MRI \cite{}
%The local non-axisymmetric stability of magnetized, self-gravitating
%disks has been treated in the shearing sheet framework \citep{} 
%framework by decomposing
%perturbations into shearing waves %ref.  
%
%global angular momentum exchange
%It is necessary to generalize the current models to non-axisymmetric
%perturbations. 
%It would be interesting to examine global spiral instabilities in a 
%magnetized disk. 
%In particular, to examine global spiral instabilities
%in a magnetized disk. 
%fu lai
